---
title: "Demo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(pureseqtmr)
```

`pureseqtmr` is a package to call PureseqTM from R.
PureseqTM predicts the topology of a membrane protein, where the topology can
be either inside, or not inside the membrane.

To be able to call PureseqTM, it needs to be installed:

```
pureseqtmr::install_pureseqtm()
```

Note that this code is not actually run, to comply with CRAN guidelines.

PureseqTM supplies some example files. Use `get_example_filenames` to
get the path to all these files:

```{r}
if (is_pureseqtm_installed()) {
  get_example_filenames()
}
```

In this example, `1bhaA.fasta` will be used. To obtain the full path,
use `get_example_filename`. `get_example_filename` will also

```{r}
if (is_pureseqtm_installed()) {
  fasta_filename <- get_example_filename("1bhaA.fasta")

}
```

Getting the topology of this protein:

```{r}
if (is_pureseqtm_installed()) {
  topology <- predict_topology(fasta_filename)
  knitr::kable(topology)
}
```

Or show the topology as a plot:

```{r}
if (is_pureseqtm_installed()) {
  plot_topology(topology)
}
```
